Research Cases

### 2025-12-15 Code/R/Research/cases_research.Rmd
More r3-research cases

```{r}
calc_errors <- function(R, pred_func, err_func, signal, seed = 5) {
  with(plan(multisession), {
    batch_recs <- function(R) {
      # p <- progressor(R)
      future_replicate(R, {
        # p()
        pred_func()
      }, simplify = "array", future.seed = seed)
    }
    if (sd == 0)
      recs <- batch_recs(2) # don't need R because no noise present. Set to 2, because with 1 will be simplified
    else
      recs <- batch_recs(R)
  })

@@

# params_grid_list: list with the parameter names as names and vectors of the parameters values as values
calc_errors_by_params <- function(params_grid_list, R, comp_func, err_func, signal, seed = 5) {
  params_grid <- expand.grid(params_grid_list)
  results <- params_grid
  results$error <- numeric(nrow(params_grid))
  q <- progressor(nrow(params_grid))
  for (i in seq(nrow(params_grid))) {
    # print(paste0(names(params_grid), " = ", params_grid[i,], collapse = ", "))
    list2env(params_grid[i,], envir = parent.frame())
    results[i,]$error <- calc_errors(R, comp_func, err_func, signal, seed)
    q()
  }
  return(results)
}
```

@@

# Assumes all amplitudes are non-zero
# TODO: This is totally wrong
calc_rank3 <- function(rate, freq, phase, complex = TRUE, tol = 1e-6) {
  if (any(c(length(ampl), length(rate), length(freq)) != length(phase)))
    stop("Amplitudes, rates, frequencies and phases all must have the same length")
  f_unique <- nrow(unique(freq))
  r_unique <- nrow(unique(rate))
  p_unique <- nrow(unique(phase))
  return(min(ncol(rate), f_unique + r_unique + p_unique - 2))
}
```

@@

## Parameters for P from 2 to 12 with one periodic
```{r}
# P <- 2
# P_case <- "_c2"
# P <- 4
# P_case <- "_c4"
# P <- 8
# P_case <- "_c8"
P <- 12
P_case <- "_c12"

@@

if (n_case == "") {
  Ls_mssa <- seq(from = max.r + 1,
                to = N - max.r - 1,
                by = 2)
  Ls_homssa = seq(from = max.r + 1,
                to = (N + 1) %/% 2,
                by = 2)
} else {
  Ls_mssa <- seq(from = max.r + 1,
                to = N - max.r - 1,
                by = 10)
  Ls_homssa = seq(from = max.r + 1,
                to = (N + 1) %/% 2,
                by = 10)
}

@@

summarise_errors <- function(err_df) {
  err_df |> mutate(zapped_error = zapsmall(error)) |> group_by(sd) |> summarise(
    best = min(zapped_error),
    avg = mean(zapped_error),
    worst = max(zapped_error)
  )
}
```

@@

```{r}
if (is.matrix(signal)) {
  print_errors_m(ssa_err)
} else {
  print_errors(ssa_err)
}
summarise_errors(ssa_err)
```

```{r}
if (is.matrix(signal)) {
  print_errors_m(tssa_err)
} else {
  print_errors(tssa_err)
}
summarise_errors(tssa_err)
```

>>>>

```{r}
calc_errors <- function(R, pred_func, err_func, signal, progbar, seed = 5) {
  with(plan(multisession), {
    batch_recs <- function(R) {
      # p <- progressor(R)
      future_replicate(R, {
        # p()
        progbar()
        pred_func()
      }, simplify = "array", future.seed = seed)
    }
    if (sd == 0)
      recs <- batch_recs(2) # don't need R because no noise present. Set to 2, because with 1 will be simplified
    else
      recs <- batch_recs(R)
  })

@@

# params_grid_list: list with the parameter names as names and vectors of the parameters values as values
calc_errors_by_params <- function(params_grid_list, R, comp_func, err_func, signal, seed = 5) {
  params_grid <- expand.grid(params_grid_list)
  results <- params_grid
  results$error <- numeric(nrow(params_grid))
  q <- progressor(nrow(params_grid) * R)
  for (i in seq(nrow(params_grid))) {
    # print(paste0(names(params_grid), " = ", params_grid[i,], collapse = ", "))
    list2env(params_grid[i,], envir = parent.frame())
    results[i,]$error <- calc_errors(R, comp_func, err_func, signal, q, seed)
    # q()
  }
  return(results)
}
```

@@

# Assumes all amplitudes are non-zero
# TODO: This is totally wrong and must not be used
calc_rank3 <- function(rate, freq, phase, complex = TRUE, tol = 1e-6) {
  if (any(c(length(ampl), length(rate), length(freq)) != length(phase)))
    stop("Amplitudes, rates, frequencies and phases all must have the same length")
  f_unique <- nrow(unique(freq))
  r_unique <- nrow(unique(rate))
  p_unique <- nrow(unique(phase))
  return(min(ncol(rate), f_unique + r_unique + p_unique - 2))
}
```

summarise_errors <- function(err_df) {
  err_df |> mutate(zapped_error = zapsmall(error)) |> group_by(sd) |> summarise(
    best = min(zapped_error),
    best_L = L[which.min(zapped_error)],
    avg = mean(zapped_error),
    worst = max(zapped_error)
  )
}
```

@@

## Parameters for P from 2 to 20 with one periodic
```{r}
# P <- 2
# P_case <- "_c2"
# P <- 4
# P_case <- "_c4"
# P <- 8
# P_case <- "_c8"
# P <- 12
# P_case <- "_c12"
# P <- 16
# P_case <- "_c16"
P <- 20
P_case <- "_c20"

@@

if (n_case == "") {
  Ls_mssa <- seq(from = max.r + 1,
                to = N,
                by = 2)
  Ls_homssa = seq(from = max.r + 1,
                to = (N + 1) %/% 2,
                by = 2)
} else {
  Ls_mssa <- seq(from = max.r + 1,
                to = N,
                by = 10)
  Ls_homssa = seq(from = max.r + 1,
                to = (N + 1) %/% 2,
                by = 10)
}

@@

@@

```{r}
if (is.matrix(signal)) {
  print_errors_m(ssa_err)
} else {
  print_errors(ssa_err)
}
(ssa_err_summ <- summarise_errors(rename(ssa_err, L = L_mssa)))
```

```{r}
if (is.matrix(signal)) {
  print_errors_m(tssa_err)
} else {
  print_errors(tssa_err)
}
(tssa_err_summ <- summarise_errors(rename(tssa_err, L = L_homssa)))
```

```{r}
((ssa_err_summ[-1, 2] - tssa_err_summ[-1, 2]) / ssa_err_summ[-1, 1]) |> rename(err_diff = best)
```
